\documentclass[11pt]{letter} % Default font size of the document, change to 10pt to fit more text

\usepackage{newcent} % Default font is the New Century Schoolbook PostScript font 
\usepackage{helvet} % Uncomment this (while commenting the above line) to use the Helvetica font

% Margins
\topmargin=-1in % Moves the top of the document 1 inch above the default
\textheight=10in % Total height of the text on the page before text goes on to the next page, this can be increased in a longer letter
\oddsidemargin=-10pt % Position of the left margin, can be negative or positive if you want more or less room
\textwidth=6.5in % Total width of the text, increase this if the left margin was decreased and vice-versa

\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right

\begin{document}

%----------------------------------------------------------------------------------------
%	ADDRESSEE SECTION
%----------------------------------------------------------------------------------------

\begin{letter}{Rob Edgecock\\rob.edgecock@stfc.ac.uk\\Tel:01235 445089\\STFC Rutherford Appleton Laboratory,\\Chilton,\\Didcot,\\OX11 0QX, UK}

%----------------------------------------------------------------------------------------
%	LETTER CONTENT SECTION
%----------------------------------------------------------------------------------------

\opening{Rob Edgecock,} 

I am writing this letter to express my interest in SEPnet Summer Placement Project "Study of high power particle production targets for neutrons and neutrino production and for medical applications". I am a Third year MPhys student at the University of Southampton.

My reason for applying this placement is that it coincides with my interest towards being an experimental particle physicist. I have a great interest in particle physics and large powerful accelerator always have interest me. I am currently taking modules like particle physics in my university as I seek to improve my understanding in the Standard Model and the physics beyond it. For my dissertation last semester, i wrote short review on the topic of neutrino oscillation and its connection with physics beyond the Standard Model. I could see that this placement would allowed me to see how theories are well applied in the physical world through the use of accelerator.

The last summer I did a placement with Oxford Instruments studying the shrink fit problem of a NbTi magnet where the results were latter used in their products that required that same technique. I am a person who is well interested in taking experimental measurements and further analyse it with aid of the computer to study the problem and comparing with theory/predictions. I always enjoy doing experiments and have taken every possible practical module that is available in my course throughout my years in university. Learning new programs to aid in my analysis is always exciting for me such as finite element analysis programs, ANSYS or using python to compute the results. See actual physics works and learning through experiments is something that I always enjoyed and wish to do so in the future.

In my last placement and in university, I am able to work independently with some supervision and able to work in groups during some of the task in my course. Meeting with people that could help in my task and learn from them is some of the experiences that I find important and hope improve my social skills with people as to overcome awkwardness between people. I am gladly to accept any interview and if the need of travel is required I would try my best to accommodate with it within my capabilities.

%-dissertation -plasmon/neutrino oscillation,physics beyond the standard model
%-oxford sepnet placement,coding experience,


\closing{Sincerely,\\Ken Keong Lee}


%\encl{Curriculum vitae, employment form} % List your enclosed documents here, comment this out to get rid of the "encl:"

%----------------------------------------------------------------------------------------

\end{letter}

\end{document}